cardinalR: Generating interesting high-dimensional data structures

### 2025-08-24 paper-cardinalR.Rmd
Updated Figure 10

hemisphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "f3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

>>>>

hemisphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.62), 
  title = "f3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)
